Why Donors Donate

### 2025-01-13 README.qmd
Marc BYU → USU

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Lewis & Clark College  
[Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Brigham Young University  
[Andrew Heiss](https://www.andrewheiss.com) • Georgia State University

>>>>

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Lewis & Clark College  
[Marc Dotson](https://occasionaldivergences.com/about) • Utah State University  
[Andrew Heiss](https://www.andrewheiss.com) • Georgia State University
